---
title: "Dynamics of Topic Exploration in Conversation"
format: 
  html:
    code-overflow: wrap
    toc: true
    embed-resources: true
editor: source
author: Helen Schmidt
date-modified: today
theme: flatly
---

# SETUP
```{r, setup, include = FALSE, message = FALSE}
# set script working directory by checking for user (HS home or lab)
if (Sys.info()[[7]] == "helenschmidt") {
  knitr::opts_knit$set(root.dir = "/Users/helenschmidt/Library/CloudStorage/GoogleDrive-helenschmidt129@gmail.com/My Drive/SANLab/Experiments/Conversation-Structure")
} else if (Sys.info()[[7]] == "tuo70125") {
  knitr::opts_knit$set(root.dir = "/Users/tuo70125/My Drive/SANLab/Experiments/Conversation-Structure")}
```

```{r, packages, include = FALSE, message = FALSE}
# packages
library(Rmisc)           # summary statistics
library(patchwork)       # combine plots
library(purrr)
library(stringr)
library(tidyverse)       # all tidy things (ggplot, dplyr, etc.)
```

```{r}
# text cleaning function
clean_text <- function(x) {
  x %>%
    str_to_lower() %>%                     # lowercase
    str_replace_all("[[:punct:]]", " ") %>%# remove punctuation
    str_squish()                           # trim + collapse extra spaces
}
```

# ANNOTATIONS
```{r}
# load dense sample annotation data
dense_df <- read.csv('/Users/helenschmidt/Library/CloudStorage/GoogleDrive-helenschmidt129@gmail.com/My Drive/SANLab/Experiments/Conversation-Structure/data/processed/dense_subset_processed.csv') |>
  select(transcript_id, PID, previous_topic, new_topic, currentUtterance, turn_id) |>
  mutate(group = "dense")
# load larger annotation data
ann_df <- read.csv('/Users/helenschmidt/Library/CloudStorage/GoogleDrive-helenschmidt129@gmail.com/My Drive/SANLab/Experiments/Conversation-Structure/data/processed/full-sample/full_sample_processed.csv') |>
  select(transcript_id, PID, previous_topic, new_topic, currentUtterance, turn_id) |>
  mutate(group = "full")

# merge
merged_df <- rbind(dense_df, ann_df)

# count annotations per utterance and transcript
merged_df <- merged_df |>
  group_by(transcript_id, currentUtterance, group) |>
  summarize(PID_count = n_distinct(PID), .groups = "drop") |>
  filter(currentUtterance != "") |>
  # apply text cleaning function
  mutate(currentUtterance_clean = clean_text(currentUtterance)) |>
  mutate(n_char = nchar(currentUtterance_clean),
         n_words = lengths(str_split(currentUtterance_clean, "\\s+")))

merged_split <- merged_df |>
  group_split(transcript_id) |>
  set_names(unique(merged_df$transcript_id))

# get list of annotated transcripts
annotated_transcripts <- unique(merged_df$transcript_id)

# number of rows where just one word is present
nrow(merged_df[merged_df$n_words == 1, ]) / nrow(merged_df)


```


# FOOTE BEST FIT

Test best fitting foote novelty combination using annotated participant data and predicted shifts.

`threshold` reflects the standard deviations away from the mean transcript foote novelty a turn has to be to count as a "predicted shift"

`kernel_size` reflects the sliding window size use to calculate foote novelty

```{r}
# load all combinations for split sentence data (main)
df_raw <- list.files(
  "/Users/helenschmidt/Library/CloudStorage/GoogleDrive-helenschmidt129@gmail.com/My Drive/SANLab/Experiments/Conversation-Structure/data/output/full-sample/foote_novelty",
  pattern = "_kernel_full_sample_tile_4_turn_split_sentences.csv$",
  full.names = TRUE) 

test <- df_raw[1:5]

# save empty data frame
evaluating_f1 <- data.frame()

# load one file at a time
for (i in test) {
  
  # load one file at a time
  df <- read.csv(i)
  # get threshold and kernel size from file name
  threshold <- str_match(i, "([0-9.]+)_foote_([0-9]+)_kernel")[2]
  kernel_size <- str_match(i, "([0-9.]+)_foote_([0-9]+)_kernel")[3]
  
  # ensure predicted shift is being treated correctly (1 = if foote_novelty >= threshold)
  df$predicted_shift_new <- ifelse(df$foote_novelty >= df$threshold, 1, 0)
  
  # only include transcripts I have corresponding annotations for
  # and make sure utterances are clean
  df <- df |>
    filter(transcript_id %in% annotated_transcripts) |>
    mutate(utterance_clean = clean_text(utterance))
  
  # flag turns that were annotated by participants
  df <- df |>
    mutate(PID_annotated = map2_lgl(transcript_id, utterance_clean, ~ {
      # define candidate strings
      candidates <- merged_split[[as.character(.x)]]
      if (is.null(candidates)) return(FALSE)
      any(str_detect(.y, fixed(candidates$currentUtterance_clean))) }))
  
  # calculate F1 scores per transcript and overall for this combination
  # true positive, false positive, false negative, precision, recall
  this_loop_f1 <- df |>
    group_by(transcript_id) |>
    summarize(
      TP = sum(predicted_shift == 1 & PID_annotated == TRUE, na.rm = TRUE),
      FP = sum(predicted_shift == 1 & PID_annotated == FALSE, na.rm = TRUE),
      FN = sum(predicted_shift == 0 & PID_annotated == TRUE, na.rm = TRUE),
    
      precision = ifelse(TP + FP == 0, NA, TP / (TP + FP)),
      recall    = ifelse(TP + FN == 0, NA, TP / (TP + FN)),
    
      F1 = ifelse(is.na(precision) | is.na(recall) | (precision + recall == 0),
                  NA, 2 * precision * recall / (precision + recall)),
      .groups = "drop") |>
    summarize(mean_F1 = mean(F1, na.rm = TRUE)) |>
    pull(mean_F1)
  
  # save info for this loop
  this_loop <- data.frame(threshold = threshold,
                          kernel_size = kernel_size,
                          F1_score = this_loop_f1)
  
  # add to overall loop
  evaluating_f1 <- rbind(evaluating_f1, this_loop)
  
} # end loop through files

# save
#write.csv(evaluating_f1, "/Users/helenschmidt/Library/CloudStorage/GoogleDrive-helenschmidt129@gmail.com/My Drive/SANLab/Experiments/Conversation-Structure/data/output/full-sample/evaluating_all_f1_scores.csv", row.names = FALSE)

```

# DATA

Based on above analysis, right now it looks like a threshold of 0.01 SD and a kernel size of 4 gives the highest F1 score (0.453).

Foote novelty threshold determined WITHIN a given conversation. Predicted topic shifts are based on turns that are a given standard deviation away from that threshold.

```{r}
# load foote novelty data
foote <- read.csv("./data/output/full-sample/foote_novelty/0.01_foote_4_kernel_full_sample_tile_4_turn_split_sentences.csv")
# load full data
df_raw <- read.csv("./data/output/full-sample/full_sample_tile_4_turn_split_sentences.csv")
# turn angle data
turn_angle <- read.csv("./data/output/full-sample/full_sample_tile_4_turn_split_sentences_turn_angle.csv")

# merge turn angle and foote novelty with full df
df <- df_raw |>
  select(transcript_id, A_start_turn, euclidean_distance) |>
  left_join(turn_angle, by = c("transcript_id", "A_start_turn")) |>
  left_join(foote |>
              select(transcript_id, A_start_turn, predicted_shift),
            by = c("transcript_id", "A_start_turn")) |>
  distinct()

# get mean/median values across transcripts
mean_values <- df |>
  summarize(mean_step = mean(euclidean_distance, na.rm = TRUE),
            mean_turn = mean(cosine_turn, na.rm = TRUE),
            median_step = median(euclidean_distance, na.rm = TRUE),
            median_turn = median(cosine_turn, na.rm = TRUE))

```

# EXAMPLE
```{r}
# plot example transcript with predicted shifts
example_transcript <- unique(df$transcript_id)[200]
example <- df |> filter(transcript_id == example_transcript)
predicted_shifts <- example |> filter(predicted_shift == 1)
threshold <- foote |> filter(transcript_id == example_transcript) |> 
  summarize(threshold = mean(threshold)) |>
  pull(threshold)
  

ggplot(example, aes(x = turn_index, y = cosine_turn)) +
  labs(title = paste0("transcript id = ", example_transcript),
       y = "Turn Angle",
       x = "Turn Index") +
  geom_hline(yintercept = threshold) +
  scale_x_continuous(expand = c(0,0)) +
  geom_point(alpha = 0) +
  geom_line() +
  geom_vline(data = predicted_shifts, aes(xintercept = turn_index),
             color = "purple", alpha = 0.2) +
  theme_classic()
```


# SHIFTS
```{r}
# build a data frame of topic events
events <- df |>
  filter(predicted_shift == 1) |>
  mutate(event_id = row_number()) |>
  select(transcript_id, turn_index, event_id)
```

```{r}
# define function to get K events before and after predicted transitions
get_windows <- function(df, events, k) {
  results <- list()
  for (i in seq_len(nrow(events))) {
    e <- events[i, ]
    data <- df |>
      filter(transcript_id == e$transcript_id) |>
      arrange(turn_index)
    idx <- which(data$turn_index == e$turn_index)
    if (length(idx) == 0) next
    
    # BEFORE window
    before <- data |>
      slice((idx - k):(idx - 1))
    if (nrow(before) == k) {
      before$relative_pos <- -k:-1
      before$event_id <- e$event_id
      results[[length(results) + 1]] <- before
    }
    
    # AFTER window
    after <- data |>
      slice((idx + 1):(idx + k))
    if (nrow(after) == k) {
      after$relative_pos <- 1:k
      after$event_id <- e$event_id
      results[[length(results) + 1]] <- after
    }
  }
  
  bind_rows(results)
  
}
```

```{r}
# 4 turns = roughly 30 seconds of conversation
# so window size = 1 (30 seconds before and after), window size = 2 (1 minute before and after)
# get average euclidean distance and cosine turn before and after predicted shifts

# define window size range
window_sizes <- 1:3

df_windows <- map_df(window_sizes, \(k) {
  w <- get_windows(df, events, k)
  w$window_size <- k
  w })

```

```{r}
# get summary information
summary_df <- df_windows |>
  mutate(period = ifelse(relative_pos < 0, "before", "after")) |>
  group_by(window_size, period) |>
  summarize(mean_step = mean(euclidean_distance, na.rm = TRUE),
            median_step = median(euclidean_distance, na.rm = TRUE),
            sd_step = sd(euclidean_distance, na.rm = TRUE),
            se_step = sd_step / sqrt(n()),
            ci_lower_step = mean_step - 1.96 * se_step,
            ci_upper_step = mean_step + 1.96 * se_step,
            mean_turn = mean(cosine_turn, na.rm = TRUE),
            median_turn = median(cosine_turn, na.rm = TRUE),
            sd_turn = sd(cosine_turn, na.rm = TRUE),
            se_turn = sd_turn / sqrt(n()),
            ci_lower_turn = mean_turn - 1.96 * se_turn,
            ci_upper_turn = mean_turn + 1.96 * se_turn,
            n = n(),
            .groups = "drop")

# plot
ggplot(summary_df, aes(x = mean_step, y = mean_turn, color = period)) +
  # plot averages across all conversations
  geom_point(data = mean_values, aes(x = mean_step, y = mean_turn), color = "black") +
  geom_vline(data = mean_values, aes(xintercept = mean_step), 
             color = "black", linetype = "dotted") +
  geom_hline(data = mean_values, aes(yintercept = mean_turn),
             color = "black", linetype = "dotted") +
  # plot before and after transitions
  geom_point(size = 2, alpha = 0.5) +
  # step SE
  geom_errorbarh(aes(xmin = ci_lower_step,
                     xmax = ci_upper_step),
                 height = 0.001) +
  # turn SE
  geom_errorbar(aes(ymin = ci_lower_turn,
                    ymax = ci_upper_turn),
                width = 0.001) +
  # facet to show range
  facet_wrap(.~window_size, axes = "all") +
  scale_color_manual(values = c("#b75044", "#eec773"), name = NULL) +
  coord_fixed() +
  theme_classic() +
  labs(x = "Moment to Moment Step Length\n(Euclidean Distance)",
       y = "Moment to Moment Turn Angle\n(Cosine Similarity)") +
  theme(legend.position = "top")

# immediate window before and after
summary_df |>
  filter(window_size == 1) |>
  ggplot(aes(x = mean_step, y = mean_turn, color = period)) +
  # plot averages across all conversations
  geom_point(data = mean_values, aes(x = mean_step, y = mean_turn), color = "black") +
  geom_vline(data = mean_values, aes(xintercept = mean_step), 
             color = "black", linetype = "dotted") +
  geom_hline(data = mean_values, aes(yintercept = mean_turn),
             color = "black", linetype = "dotted") +
  # plot before and after transitions
  geom_point(size = 3, alpha = 0.5) +
  # step SE
  geom_errorbarh(aes(xmin = ci_lower_step,
                     xmax = ci_upper_step),
                 height = 0.001) +
  # turn SE
  geom_errorbar(aes(ymin = ci_lower_turn,
                    ymax = ci_upper_turn),
                width = 0.001) +
  scale_color_manual(values = c("#b75044", "#1e475c"), name = NULL) +
  coord_fixed() +
  theme_classic() +
  labs(x = "Moment to Moment Step Length\n(Euclidean Distance)",
       y = "Moment to Moment Turn Angle\n(Cosine Similarity)") +
  theme(legend.position = "top")

```



```{r}
# identify "blocks" when predicted_shift = 1 for multiple rows
# rle = run length encoding
df <- df |>
  arrange(transcript_id, turn_index) |>
  group_by(transcript_id) |>
  mutate(shift_run = with(rle(predicted_shift), rep(seq_along(lengths), lengths)),
         shift_block = ifelse(predicted_shift == 1, shift_run, NA)) |>
  ungroup()

# get average step and turn across all transcripts
mean_values <- df |>
  summarize(mean_step = mean(euclidean_distance, na.rm = TRUE),
            mean_turn = mean(cosine_turn, na.rm = TRUE),
            median_step = median(euclidean_distance, na.rm = TRUE),
            median_turn = median(cosine_turn, na.rm = TRUE))

# get topic transitions
topics <- df |>
  filter(predicted_shift == 1) |>
  group_by(transcript_id, shift_block) |>
  summarize(start_index = min(turn_index),
            end_index = max(turn_index),
            .groups = "drop")

# define function to get K number of events before and after transitions
get_windows <- function(df, topics, k) {
  results <- list() 
  for (i in seq_len(nrow(topics))) {
    t <- topics[i, ]
    data <- df |>
      filter(transcript_id == t$transcript_id) 
    
    # before window
    before <- data |>
      filter(turn_index < t$start_index) |>
      arrange(desc(turn_index)) |>
      slice_head(n = k)
    
    if (nrow(before) == k && all(before$predicted_shift == 0)) {
      before$relative_pos <- -seq_len(k)
      before$event_id <- i
      results[[length(results) + 1]] <- before }
    
    # after window
    after <- data |>
      filter(turn_index > t$end_index) |>
      arrange(turn_index) |>
      slice_head(n = k)
    
    if (nrow(after) == k && all(after$predicted_shift == 0)) {
      after$relative_pos <- seq_len(k)
      after$event_id <- i
      results[[length(results) + 1]] <- after}
    
  } # end topic loop
  
  bind_rows(results)
  
} # end function

```

# PLOT
```{r}
# 4 turns = roughly 30 seconds of conversation
# so window size = 1 (30 seconds before and after), window size = 2 (1 minute before and after)
# get average euclidean distance and cosine turn before and after predicted shifts

# define window size range
window_sizes <- 1:3

df_windows <- map_df(window_sizes, ~{
  w <- get_windows(df, topics, .x)
  w$window_size <- .x
  w})

# get summary
df_summary <- df_windows |>
  group_by(window_size, relative_pos) |>
  summarize(mean_step = mean(euclidean_distance, na.rm = TRUE),
            se_step = sd(euclidean_distance, na.rm = TRUE) / sqrt(n()),
            mean_turn = mean(cosine_turn, na.rm = TRUE),
            se_turn = sd(cosine_turn, na.rm = TRUE) / sqrt(n()),
            n = n(),
            .groups = "drop")

summary_collapsed <- df_windows |>
  mutate(period = ifelse(relative_pos < 0, "before", "after")) |>
  group_by(window_size, period) |>
  summarize(mean_step = mean(euclidean_distance, na.rm = TRUE),
            se_step = sd(euclidean_distance, na.rm = TRUE) / sqrt(n()),
            mean_turn = mean(cosine_turn, na.rm = TRUE),
            se_turn = sd(cosine_turn, na.rm = TRUE) / sqrt(n()),
            n = n(),
            .groups = "drop")

# add data point for at transition too
at_transition <- df |>
  filter(predicted_shift == 1) |>
  summarize(mean_step = mean(euclidean_distance, na.rm = TRUE),
            se_step = sd(euclidean_distance, na.rm = TRUE) / sqrt(n()),
            mean_turn = mean(cosine_turn, na.rm = TRUE),
            se_turn = sd(cosine_turn, na.rm = TRUE) / sqrt(n()),
            n = n(),
            .groups = "drop")

at_transition <- data.frame(window_size = c(1:6),
                            period = "at",
                            mean_step = at_transition$mean_step,
                            se_step = at_transition$se_step,
                            mean_turn = at_transition$mean_turn,
                            se_turn = at_transition$se_turn, 
                            n = at_transition$n)

summary_collapsed <- rbind(summary_collapsed, at_transition)
summary_collapsed$period <- factor(summary_collapsed$period,
                                   levels = c("before", "at", "after"))

```

```{r}
# plot
ggplot(summary_collapsed, aes(x = mean_step, y = mean_turn, color = period)) +
  # plot averages across all conversations
  geom_point(data = mean_values, aes(x = mean_step, y = mean_turn), color = "black") +
  geom_vline(data = mean_values, aes(xintercept = mean_step), 
             color = "black", linetype = "dotted") +
  geom_hline(data = mean_values, aes(yintercept = mean_turn),
             color = "black", linetype = "dotted") +
  # plot before and after transitions
  geom_point(size = 3) +
  # step SE
  geom_errorbarh(aes(xmin = mean_step - se_step,
                     xmax = mean_step + se_step),
                 height = 0.001) +
  # turn SE
  geom_errorbar(aes(ymin = mean_turn - se_turn,
                    ymax = mean_turn + se_turn),
                width = 0.001) +
  # facet to show range
  facet_wrap(.~window_size, axes = "all") +
  scale_color_manual(values = c("#1e475c", "#b75044", "#eec773"), name = NULL) +
  coord_fixed() +
  theme_classic() +
  labs(x = "Moment to Moment Step Length\n(Euclidean Distance)",
       y = "Moment to Moment Turn Angle\n(Cosine Similarity)") +
  theme(legend.position = "top")

# just one turn example
summary_collapsed |>
  filter(window_size == 1) |>
  ggplot(aes(x = mean_step, y = mean_turn, color = period)) +
  # plot averages across all conversations
  geom_point(data = mean_values, aes(x = mean_step, y = mean_turn), color = "black") +
  geom_vline(data = mean_values, aes(xintercept = mean_step), 
             color = "black", linetype = "dotted") +
  geom_hline(data = mean_values, aes(yintercept = mean_turn),
             color = "black", linetype = "dotted") +
  # plot before and after transitions
  geom_point(size = 4) +
  # step SE
  geom_errorbarh(aes(xmin = mean_step - se_step,
                     xmax = mean_step + se_step),
                 height = 0.0005) +
  # turn SE
  geom_errorbar(aes(ymin = mean_turn - se_turn,
                    ymax = mean_turn + se_turn),
                width = 0.0005) +
  scale_color_manual(values = c("#1e475c", "#b75044", "#eec773"), name = NULL) +
  coord_fixed() +
  theme_classic() +
  labs(x = "Moment to Moment Step Length\n(Euclidean Distance)",
       y = "Moment to Moment Turn Angle\n(Cosine Similarity)") +
  theme(legend.position = "top")

```

```{r}


# merge turn angle and foote novelty with full df
df <- df_raw |>
  select(transcript_id, A_start_turn, euclidean_distance) |>
  left_join(turn_angle, by = c("transcript_id", "A_start_turn")) |>
  left_join(
    foote |>
      select(transcript_id, A_start_turn, predicted_shift),
    by = c("transcript_id", "A_start_turn")
  ) |>
  distinct()

# identify "blocks" when predicted_shift = 1 for multiple rows
df <- df |>
  arrange(transcript_id, turn_index) |>
  group_by(transcript_id) |>
  mutate(
    shift_run = with(rle(predicted_shift), rep(seq_along(lengths), lengths)),
    shift_block = ifelse(predicted_shift == 1, shift_run, NA)
  )

# get average step and turn across all transcripts
mean_values <- df |>
  ungroup() |>
  summarize(
    mean_step = mean(euclidean_distance, na.rm = TRUE),
    mean_turn = mean(cosine_turn, na.rm = TRUE)
  )

# get topic transitions (events)
topics <- df |>
  filter(predicted_shift == 1) |>
  group_by(transcript_id, shift_block) |>
  summarize(
    start_index = min(turn_index),
    end_index   = max(turn_index),
    .groups = "drop"
  )

df_split <- df |> group_by(transcript_id) |> group_split()
#df_split <- df |> group_split(transcript_id)
names(df_split) <- df |> group_keys() |> pull(transcript_id)

# function to get windows
get_windows <- function(df_split, topics, k) {

  results <- list()

  for (i in seq_len(nrow(topics))) {

    t <- topics[i, ]

    data <- df_split[[as.character(t$transcript_id)]]

    # BEFORE
    before <- data |>
      filter(turn_index < t$start_index) |>
      arrange(desc(turn_index)) |>
      slice_head(n = k)

    if (nrow(before) == k && all(before$predicted_shift == 0)) {
      before$relative_pos <- -seq_len(k)
      before$event_id <- i
      results[[length(results) + 1]] <- before
    }

    # AFTER
    after <- data |>
      filter(turn_index > t$end_index) |>
      arrange(turn_index) |>
      slice_head(n = k)

    if (nrow(after) == k && all(after$predicted_shift == 0)) {
      after$relative_pos <- seq_len(k)
      after$event_id <- i
      results[[length(results) + 1]] <- after
    }
  }

  bind_rows(results)
}

# define window sizes
window_sizes <- 1:5

# extract windows
df_windows <- map_df(window_sizes, ~{
  w <- get_windows(df_split, topics, .x)
  w$window_size <- .x
  w
})

# 🔑 EVENT-LEVEL aggregation (fixes SE issue)
event_level <- df_windows |>
  mutate(period = ifelse(relative_pos < 0, "before", "after")) |>
  group_by(window_size, event_id, period) |>
  summarize(
    step = mean(euclidean_distance, na.rm = TRUE),
    turn = mean(cosine_turn, na.rm = TRUE),
    .groups = "drop"
  )

# final summary (SE across events)
summary_collapsed <- event_level |>
  group_by(window_size, period) |>
  summarize(
    mean_step = mean(step),
    se_step   = sd(step) / sqrt(n()),
    mean_turn = mean(turn),
    se_turn   = sd(turn) / sqrt(n()),
    n = n(),
    .groups = "drop"
  )

# plot
ggplot(summary_collapsed,
       aes(x = mean_step, y = mean_turn, color = period)) +

  # overall mean reference
  geom_point(
    data = mean_values,
    aes(x = mean_step, y = mean_turn),
    color = "black"
  ) +
  geom_vline(
    data = mean_values,
    aes(xintercept = mean_step),
    color = "black",
    linetype = "dotted"
  ) +
  geom_hline(
    data = mean_values,
    aes(yintercept = mean_turn),
    color = "black",
    linetype = "dotted"
  ) +

  # before vs after points
  geom_point(size = 3) +

  # horizontal SE (euclidean)
  geom_errorbarh(
    aes(
      xmin = mean_step - se_step,
      xmax = mean_step + se_step
    ),
    height = 0.02
  ) +

  # vertical SE (cosine)
  geom_errorbar(
    aes(
      ymin = mean_turn - se_turn,
      ymax = mean_turn + se_turn
    ),
    width = 0.02
  ) +

  facet_wrap(. ~ window_size) +
  scale_color_manual(values = c("#b75044", "#eec773"), name = NULL) +
  coord_fixed() +
  theme_classic() +
  labs(
    x = "Moment to Moment Step Length\n(Euclidean Distance)",
    y = "Moment to Moment Turn Angle\n(Cosine Similarity)"
  ) +
  theme(legend.position = "top")
```

